\pkg{Rgbp}: An R Package for Gaussian, Poisson, and Binomial Hierarchical Modeling

### 2013-08-14 jss/article.tex

\subsection[Poisson-Gamma]{Poisson-Gamma (``p''=Poisson data)}
\code{gbp} is also able to build a Poisson-Gamma hierarchical model. Note that a constant, $1/r$, multiplied to the Gamma distribution below is a scale and a square bracket [, ] below indicates [mean, variance] of a distribution. For notational consistency, let's define $y_{j}\equiv z_{j} / n_{j}$ as the unbiased estimate of $\lambda_{j}$, where $j=1, \ldots, k$.
\begin{equation}
z_{j}\vert \lambda_{j} \stackrel{ind}{\sim}\textrm{Poisson}(n_{j}\lambda_{j}),
\end{equation}
\begin{equation}\label{gammaprior}
\lambda_{j}\vert \beta, r\stackrel{ind}{\sim}\frac{1}{r}\textrm{Gamma}(r\lambda_{0j})\sim \textrm{Gamma} \left[\lambda_{0j}, ~\frac{\lambda_{0j}}{r} \right],
\end{equation}

where $\log(\lambda_{0j}) =x_{j}'\beta$, $j=1, \ldots, k$, with two unknown hyper-parameters, $r$ and $\beta$. The posterior distribution of this Poisson-Gamma model is
\begin{equation} \label{gammapost}
\lambda_{j}\vert \textbf{y}, \beta, r \stackrel{ind}{\sim}\frac{1}{r + n_{j}}\textrm{Gamma}(r\lambda_{0j} + n_{j}y_{j})\sim\textrm{Gamma} \left[\lambda^{\ast}_{j},~\frac{\lambda^{\ast}_{j}}{r+n_{j}} \right],
\end{equation}

@@

where $\log(\frac{p_{0j}}{1-p_{0j}}) =x_{j}'\beta, ~j=1, \ldots, k$ and $r$ and $\beta$ are two unknown hyper-parameters. Then corresponding posterior distribution given  $r$ and $\beta)$ is
\begin{equation} \label{betapost}
p_{j}\vert \textbf{y}, \beta, r \stackrel{ind}{\sim}\textrm{Beta}(rp_{0j}+n_{j}y_{j},~r(1-p_{0j})+n_{j}(1-y_{j}))\sim\textrm{Beta}\bigg[p^{\ast}_{j},~ \frac{p^{\ast}_{j}(1-p^{\ast}_{j})}{r+n_{j}+1}\bigg],
\end{equation}
where $p^{\ast}_{j}\equiv(1-B_{j})y_{j}+B_{j}p_{0j}$, $B_{j}\equiv r/ (r+n_{j})$, and $y_{j}\equiv z_{j} / n_{j}$, $j=1,\ldots,k$.

\subsection[Hyper-prior Distribution]{Hyper-prior Distribution}
A hyper-prior distribution is a distribution assigned to the second-level parameters. With the goal of objectivity in mind our choice for hyper priors with \code{gbp} assumes the following non-informative hyper-prior distributions:
\begin{equation}
\beta \sim \textrm{Uniform on}~ \mathbf{R}^{m}~~\textrm{and}~~A \sim \textrm{Uniform}(0, \infty) ~~(\textrm{or} ~\frac{1}{r}\sim \textrm{Uniform}(0, \infty)),
\end{equation}

where $m$ is the number of regression coefficients. As for $\beta$, the flat non-informative distribution above is a common choice. In the Gaussian case, the flat prior distribution on the second-level variance $A$ is chosen to produce good repeated sampling properties for point and interval estimates of the true parameters $\{\mu_{j}\}$, and to have its posterior propriety when $k\ge m+3$ \citep{2011}. In the other two cases, Poisson and Binomial, the distribution of $\frac{1}{r}$ induces the same improper prior distribution on shrinkages ($B_{j}$) as does $A$ with Unif($0, \infty$) for the Gaussian. We will show the efficiency of this assignment  in the examples in section 5.

@@

\subsection[ADM]{Approximation via Adjustment for Density Maximization}
It is noted that the shrinkage factors ($B_1, \ldots B_k$) are a function of the second-level variance component, \emph{i.e.}, $B_{j}\equiv V_{j}/(V_{j}+A)=B_{j}(A)$ for Gaussian and $B_{j}\equiv r/(r+n_{j})=B_{j}(r)$ for Poisson and Binomial models. A common approach to approximate the distribution of $B_{j}$ is to find its MLE $\hat{B}_{j}(\hat{A}_{MLE})$ (or  $\hat{B}_{j}(\hat{r}_{MLE})$) and to use its asymptotic Normality. But MLE can result in estimates lying on the boundary of the parameter space, and its asymptotic Gaussian distribution is defined on $(-\infty, \infty)$ whereas $B_{j}$ is bounded between 0 and 1.

To continue with a maximization-based estimation procedure but to steer clear of aforementioned boundary issues we make use of adjustment for density maximization (ADM) \citep{carl1988, 1997, 2011}. For our purposes we approximate the posterior distribution of a shrinkage factor with a Beta distribution, which allows us to finally obtain estimates of the posterior moments, \emph{i.e.}  of $E(B_{j}\vert\textrm{data})$ and $Var(B_{j}\vert\textrm{data})$, without the boundary issues that MLE encounters. See \cite{2011}.
>>>>>>> 3c705aa06ceadc1c8ebef0446e4039dc98866b97

@@

Using the posterior mean and variance estimates of $B_{j}$, \pkg{Rgbp} estimates the posterior mean and variance of true parameters given only the data ($\textbf{y}$). Taking the Normal-Normal model as an example, it estimates $E(\mu_{j}\vert \textbf{y})$ and $Var(\mu_{j}\vert \textbf{y})$ by the following identities
\begin{eqnarray}
E(\mu_{j}\vert \textbf{y}) & = & E(E(\mu_{j}\vert \textbf{y}, \beta, A)\vert \textbf{y}), \\
Var(\mu_{j}\vert \textbf{y}) & = & E(Var(\mu_{j}\vert \textbf{y}, \beta, A)\vert \textbf{y})+Var(E(\mu_{j}\vert \textbf{y}, \beta, A)\vert \textbf{y}),
\end{eqnarray}  
where both $E(\mu_{j}\vert \textbf{y}, \beta, A)$ and $Var(\mu_{j}\vert \textbf{y}, \beta, A)$ are linear functions of the shrinkage factors as specified in (\ref{normalpost}).

@@

Once we make sure that the hierarchical modeling can be appropriate for our data, the following question will be about the validity of interval estimates, the final product of this hierarchical modeling. ``Does the 95\% (can be specified differently) confidence interval obtained via this Bayesian model-fitting process achieve 95\% confidence level  for any true parameter values?'' \pkg{Rgbp} has a function called \code{coverage} to answer this question and it comprises of two parts, generating pseudo-dataset and estimating coverage probability.

@@

For this purpose, data were gathered from 31 hospitals in NY composed of the number of deaths ($z$) within a month of CABG surgeries and total number of patients ($n$) receiving CABG surgeries in each hospital. Using these data, \pkg{Rgbp} provides point and interval estimates of the true death ratio for each hospital so that one can choose the most reliable hospital. The data can be loaded into R using the following code:
\begin{CodeChunk}
\begin{CodeInput}
R> z <- c( 3, 2, 5, 11, 9, 12, 12, 4, 10, 13, 14, 7, 12, 11, 13, 22, 15, 
          11, 14, 11, 16, 14, 9, 15, 13, 35, 26, 25, 20, 35, 27)
R> n <- c(67, 68, 210, 256, 269, 274, 278, 295, 347, 349, 358, 396, 431,
         441, 477, 484, 494, 501, 505, 540, 563, 593, 602, 629, 636, 729,
         849, 914, 940, 1193, 1340)
\end{CodeInput}
\end{CodeChunk}
or
\begin{CodeChunk}
\begin{CodeInput}
R> data(hospitals)
R> z <- hospitals$d
R> n <- hospitals$n
\end{CodeInput}
\end{CodeChunk}

Note that throughout this paper, the symbol `\code{R>}' represents a command prompt that you should not type on \proglang{R}.

@@

Next, \code{gbp} will help us fit the Poisson hierarchical model with the Gamma conjugate prior distribution on the true death rate $\lambda_{j}$ whose mean is 0.020 ($\lambda_{0}=0.020$) as described in the section 2.2. For reference, the number of regression coefficients ($m$) is 0 because we do not need to estimate the prior mean via log-linear regression (see section 3.2).
\begin{CodeChunk}
\begin{CodeInput}
R> p <- gbp(z, n, mean.PriorDist = 0.02, model = "poisson")
R> p
\end{CodeInput}
\begin{CodeOutput}
Summary for each unit (sorted by n):

@@

The output contains information about observed death ratio ($y_{j}$), caseload ($n_{j}$), known prior mean ($\lambda_{0}$), shrinkage estimate ($\hat{B}_{j}$), lower bound of interval estimate ($\hat{\lambda}_{j, low}$), posterior mean ($\hat{\lambda}=E(\lambda_{j}\vert \textbf{y})$), upper bound of interval estimate ($\hat{\lambda}_{j, upp}$), and standard deviation of posterior distribution ($sd(\lambda_{j}\vert \textbf{y})$).

@@

  post.mode.alpha post.sd.alpha
1          -5.818         0.411
\end{CodeOutput}
\end{CodeChunk}
From the output of \code{Rgbp} we can easily calculate $\hat{r}=\textrm{exp}(5.818)=336$, which is a good indicator of how valuable and informative the hypothetical second-level hierarchy is. It means that observed sample means of hospitals whose caseloads are less than 336 will shrink toward the prior mean (0.020) more than 50\%. For example, the shrinkage estimate of the first hospital ($\hat{B}_{1}= 0.834$) was calculated by 336 / (336 + 67), where 67 is its caseload ($n_{1}$), and its posterior mean is $(1-0.834)*0.045 + 0.834 * 0.020=0.024$. As for this hospital, using more information from the prior distribution is an appropriate choice because the observed amount of information (67) is far less than the amount of state-level information (336).

To obtain a graphical summary the function \code{plot} can be used, as seen in \ref{fig:hospshr}.

\begin{CodeChunk}
\begin{CodeInput}
R> plot(p)
\end{CodeInput}
\end{CodeChunk}
\begin{figure}[h]
\begin{center}
\includegraphics[scale=0.25]{hospital1.png}
\caption{Shrinkage plot and 95\% interval plot}
\label{fig:hospshr}
\end{center}
\end{figure}

@@

Also, \code{gbp} can provide interval estimates with different confidence levels, for example 90\%,  and the appropriate code adjustment is `\code{R> p <- gbp(z, n, Alpha = 0.9, mean.PriorDist = 0.02, model = "pr")}.'  Then, the below code will evaluate whether interval estimates achieve the 90\% confidence level.

@@

In Figure \ref{fig:hospitalcoverage} we see three lines; one is a red line connecting Rao-Blackwellized unbiased estimates for 31 hospitals; another is a dashed blue line connecting simple unbiased estimates for those hospitals; a black horizontal line indicating the confidence level, 0.95.

The estimated overall average coverage rate is 0.950 from both Rao-Blackwellized and simple unbiased estimates. This result shows that the interval estimates for this particular dataset accurately achieves 95\% confidence under repeated sampling. Note that this estimate depends on the given true value of $r$ and the assumption that the model is true.

If we want to check average Rao-Blackwellized unbiased estimates of coverage rate for each hospital, the following code gives us 31 estimates.
\begin{CodeChunk}
\begin{CodeInput}
R> pcv$coverageRB
\end{CodeInput}
\begin{CodeOutput}
 [1] 0.950 0.950 0.950 0.951 0.950 0.950 0.951 0.950 0.950 0.950 0.951 0.951 
[13] 0.950 0.950 0.950 0.950 0.951 0.950 0.950 0.950 0.950 0.951 0.950 0.950 
[25] 0.951 0.950 0.951 0.950 0.951 0.951 0.950
\end{CodeOutput}
\end{CodeChunk}

As for average simple unbiased estimates of coverage rate for each hospital, we can type the code below to obtain 31 estimates. 
\begin{CodeChunk}
\begin{CodeInput}
R> pcv$coverageS
\end{CodeInput}
\begin{CodeOutput}
 [1] 0.949 0.953 0.946 0.955 0.957 0.939 0.956 0.957 0.944 0.952 0.956 0.955 
[13] 0.949 0.957 0.948 0.954 0.951 0.934 0.956 0.943 0.959 0.952 0.949 0.964 
[25] 0.949 0.953 0.941 0.938 0.941 0.956 0.951
\end{CodeOutput}
\end{CodeChunk}

The last thing to mention is the accuracy of Rao-Blackwellized unbiased estimates compared to that of simple one. Taking the first hospital as an example, we can calculate the sample variance of 1,000 Rao-Blackwellized unbiased estimates for the first hospital and that of 1,000 simple ones by typing following code. For reference, \code{raw.resultRB} and \code{raw.resultS} in \code{pcv} contains all the individual simulation results.
\begin{CodeChunk}
\begin{CodeInput}
R> var(pcv$raw.resultRB[1, ])
\end{CodeInput}
\begin{CodeOutput}
 [1] 0.002031225
\end{CodeOutput}
\begin{CodeInput}
R> var(pcv$raw.resultS[1, ])
\end{CodeInput}
\begin{CodeOutput}
 [1] 0.04844745
\end{CodeOutput}
\end{CodeChunk}

@@

The Education Testing Service (ETS) conducted randomized experiments in eight separate schools (group) to test whether students (unit) SAT scores are effected by coaching. The dataset contains the estimated coaching effects on SAT scores ($y_{j}, j=1, \ldots, 8$) and standard errors ($se_{j}, j=1, \ldots, 8$) of the eight schools \citep{1981}.
\begin{CodeChunk}
\begin{CodeInput}
R> y  <- c(12, -3, 28,  7,  1,  8, 18, -1)
R> se <- c(18, 16, 15, 11, 11, 10, 10,  9)
\end{CodeInput}
\end{CodeChunk}

@@

\begin{CodeChunk}
\begin{CodeInput}
R> data(schools)
R> g <- gbp(y, se, model = "gaussian")
R> g
\end{CodeInput}
\begin{CodeOutput}
Summary for each unit (sorted by se):

@@

As seen in Figure \ref{fig:schoolcoverage} the desired $95\%$ confidence (horizontal line at 0.95) is achieved (actually, exceeded) for each school in this example. Here, all the coverage estimates depend on the given true values of $A$ and $\beta_{0}$, and the assumption that the model is true.

Average Rao-Blackwellized unbiased estimates of coverage rate for each school can be seen as below.
\begin{CodeChunk}
\begin{CodeInput}
R> gcv$coverageRB
\end{CodeInput}
\begin{CodeOutput}
 [1] 0.966 0.957 0.966 0.962 0.960 0.961 0.960 0.969
\end{CodeOutput}
\end{CodeChunk}

As for average simple unbiased estimates of coverage rate for each school, 
\begin{CodeChunk}
\begin{CodeInput}
R> gcv$coverageS
\end{CodeInput}
\begin{CodeOutput}
[1] 0.970 0.943 0.957 0.968 0.956 0.969 0.961 0.976
\end{CodeOutput}
\end{CodeChunk}

Finally  when it comes to the first school,  Rao-Blackwellized unbiased estimate is about 24 times more accurate than simple one. It is based on the ratio of the sample variances of individual 1,000 estimates from two approaches.
\begin{CodeChunk}
\begin{CodeInput}
R> var(pcv$raw.resultS[1, ]) / var(pcv$raw.resultRB[1, ])
\end{CodeInput}
\begin{CodeOutput}
 [1] 23.85134
\end{CodeOutput}
\end{CodeChunk}

@@

The following dataset from the New York Times published on 26 April 1970 contains information on the batting averages of 18 major league baseball players through their first 45 official at-bats of the 1970 season \citep{1975}. In addition one covariate relating to the position of each player was observed and for illustrative purposes, we transform this variable into a binary indicator (1 if a player was an outfielder and 0 otherwise).
\begin{CodeChunk}
\begin{CodeInput}
R> z <- c(18, 17, 16, 15, 14, 14, 13, 12, 11, 11, 10, 10, 10, 10, 10,  9,  8,  7)
R> n <- c(45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45)
R> x <- c( 1,  1,  1,  1,  1,  0,  0,  0,  0,  1,  0,  0,  0,  1,  1,  0,  0,  0) 
\end{CodeInput}
\end{CodeChunk}

@@

In problems where a covariate is present \code{gbp} provides a regression summary (in this example logistic regression)
\begin{CodeChunk}
\begin{CodeInput}
R> summary(b)
\end{CodeInput}
\begin{CodeOutput}
Main summary:

@@

We see that the two prior means distinguishing outfielders from other positions were significantly different (p-value = 0.038), supporting our initial belief. The positive sign of $\hat{\beta}_{1}$ indicates that the mean batting average for all the outfielders tends to be higher than that for those in the other positions.

Now, let's see following shrinkage and 95\% interval plots for more intuition. It is obvious that sample means (empty dots) on the upper horizontal line shrink towards two different means, 0.310 and 0.233. For reference, the red line symbols on dots are for when two or more points have the same mean and are plotted over each other. For example, five players (from the 11th player to the 15th) have the same sample mean (0.222) and at this point on the upper horizontal line, there are short red lines toward five directions.

\begin{CodeChunk}
\begin{CodeInput}
R> plot(b)
\end{CodeInput}
\end{CodeChunk}
\begin{figure}[h]
\begin{center}
\includegraphics[scale=0.3]{baseball1.png}
\caption{Shrinkage plot and 95\% interval plot}
\label{fig:baseball}
\end{center}
\end{figure}

@@

Then, how much can we trust these interval estimates? The following frequency method checking that regards the estimated values, $\hat{r}$ (=112.95) and $\hat{\beta}~(=(-1.194, ~0.389)^{T})$, as true values when it generates pseudo-datasets will answer it. For reference, if we want to try different true parameters, the appropriate code will be \code{coverage(b, A.or.r = 100, reg.coef = c(-1, 0.2), nsim = 1000)} instead of below one.

>>>>

\subsection[Poisson-Gamma]{Poisson-Gamma (``p''=Poisson data)}\label{poissonsubsec}
\code{gbp} is also able to build a Poisson-Gamma hierarchical model. Note that a constant, $1/r$, multiplied to the Gamma distribution below is a scale and a square bracket [, ] below indicates [mean, variance] of a distribution. For notational consistency, let's define $y_{j}\equiv z_{j} / n_{j}$ as the unbiased estimate of $\lambda_{j}$, where $j=1, \ldots, k$.
\begin{equation}
z_{j}\vert \lambda_{j} \stackrel{ind}{\sim}\textrm{Poisson}(n_{j}\lambda_{j}),
\end{equation}
\begin{equation}\label{gammaprior}
\lambda_{j}\vert \beta, r\stackrel{ind}{\sim}\frac{1}{r}\textrm{Gamma}(r\lambda_{0j})\sim \textrm{Gamma} \left[\lambda_{0j}, ~\frac{\lambda_{0j}}{r} \right],
\end{equation}

where $\log(\lambda_{0j}) =x_{j}'\beta$, $j=1, \ldots, k$, with two unknown hyper-parameters, $\beta$ and $r$. The posterior distribution of this Poisson-Gamma model given these hyper-parameters is
\begin{equation} \label{gammapost}
\lambda_{j}\vert \textbf{y}, \beta, r \stackrel{ind}{\sim}\frac{1}{r + n_{j}}\textrm{Gamma}(r\lambda_{0j} + n_{j}y_{j})\sim\textrm{Gamma} \left[\lambda^{\ast}_{j},~\frac{\lambda^{\ast}_{j}}{r+n_{j}} \right],
\end{equation}

@@

where $\log(\frac{p_{0j}}{1-p_{0j}}) =x_{j}'\beta, ~j=1, \ldots, k$ and $\beta$ and $r$ are two unknown hyper-parameters. Then corresponding posterior distribution given  $\beta$ and $r$ is
\begin{equation} \label{betapost}
p_{j}\vert \textbf{y}, \beta, r \stackrel{ind}{\sim}\textrm{Beta}(rp_{0j}+n_{j}y_{j},~r(1-p_{0j})+n_{j}(1-y_{j}))\sim\textrm{Beta}\bigg[p^{\ast}_{j},~ \frac{p^{\ast}_{j}(1-p^{\ast}_{j})}{r+n_{j}+1}\bigg],
\end{equation}
where $p^{\ast}_{j}\equiv(1-B_{j})y_{j}+B_{j}p_{0j}$, $B_{j}\equiv r/ (r+n_{j})$, and $y_{j}\equiv z_{j} / n_{j}$, $j=1,\ldots,k$.

\subsection[Hyper-prior Distribution]{Hyper-prior Distribution}
A hyper-prior distribution is a distribution assigned to the second-level parameters. With the goal of objectivity in mind our choice for hyper-priors with \code{gbp} assumes the following non-informative hyper-prior distributions:
\begin{equation}
\beta \sim \textrm{Uniform on}~ \mathbf{R}^{m}~~\textrm{and}~~A \sim \textrm{Uniform}(0, \infty) ~~(\textrm{or} ~\frac{1}{r}\sim \textrm{Uniform}(0, \infty)),
\end{equation}

where $m$ is the number of regression coefficients. As for $\beta$, the flat non-informative distribution above is a common choice. In the Gaussian case, the flat prior distribution on the second-level variance $A$ is chosen to produce good repeated sampling properties for point and interval estimates of the true parameters $\{\mu_{j}\}$, and to have its posterior propriety when $k\ge m+3$ \citep{2011}. In the other two cases, Poisson and Binomial, the distribution of $\frac{1}{r}$ induces the same improper prior distribution on shrinkages ($B_{j}$) as does $A$ with Uniform($0, \infty$) for the Gaussian. We will show the efficiency of this assignment  in the examples in section 5.

@@

\subsection[ADM]{Approximation via Adjustment for Density Maximization}\label{ADM}
It is noted that the shrinkage factors ($B_1, \ldots B_k$) are a function of the second-level variance component, \emph{i.e.}, $B_{j}\equiv V_{j}/(V_{j}+A)=B_{j}(A)$ for Gaussian and $B_{j}\equiv r/(r+n_{j})=B_{j}(r)$ for Poisson and Binomial models. A common approach to approximate the distribution of $B_{j}$ is to find its MLE $\hat{B}_{j}(\hat{A}_{MLE})$ (or  $\hat{B}_{j}(\hat{r}_{MLE})$) and to use its asymptotic Normality. But its asymptotic Gaussian distribution is defined on $(-\infty, \infty)$ whereas $B_{j}$ is bounded between 0 and 1, and MLE can result in estimates lying on the boundary of the parameter space.

To continue with a maximization-based estimation procedure but to steer clear of aforementioned boundary issues we make use of adjustment for density maximization (ADM) \citep{carl1988, 1997, 2011}. For our purposes we approximate the posterior distribution of a shrinkage factor with a Beta distribution, which allows us to finally obtain estimates of the posterior moments, \emph{i.e.}  of $E(B_{j}\vert\textrm{data})$ and $Var(B_{j}\vert\textrm{data})$, without the boundary issues that MLE encounters. See \cite{2011}.

@@

Using the posterior mean and variance estimates of $B_{j}$, \pkg{Rgbp} estimates the posterior mean and variance of true parameters given only the data ($\textbf{y}$). Taking the Normal-Normal model as an example, it estimates $E(\mu_{j}\vert \textbf{y})$ and $Var(\mu_{j}\vert \textbf{y})$ by the following identities
\begin{eqnarray}
E(\mu_{j}\vert \textbf{y}) & = & E(E(\mu_{j}\vert \textbf{y}, \beta, A)\vert \textbf{y}), \\
Var(\mu_{j}\vert \textbf{y}) & = & E(Var(\mu_{j}\vert \textbf{y}, \beta, A)\vert \textbf{y})+Var(E(\mu_{j}\vert \textbf{y}, \beta, A)\vert \textbf{y}),
\end{eqnarray}  
where both $E(\mu_{j}\vert \textbf{y}, \beta, A)$ and $Var(\mu_{j}\vert \textbf{y}, \beta, A)$ are linear functions of the shrinkage factors as specified in (\ref{normalpost}). We then estimate $E(\mu_{j}\vert \textbf{y})$ and $Var(\mu_{j}\vert \textbf{y})$ by plugging-in approximately estimated two posterior moments of shrinkage factors.

@@

Once we make sure that the hierarchical modeling can be appropriate for our data, the following question will be about the validity of interval estimates, the final product of this hierarchical modeling. ``Does the 95\% (can be specified differently) confidence interval obtained via this Bayesian model-fitting process achieve 95\% confidence level  for any true parameter values?'' \pkg{Rgbp} has a function called \code{coverage} to answer this question and it comprises of two parts, generating pseudo-datasets and estimating coverage probabilities.

@@

For this purpose, data were gathered from 31 hospitals in NY composed of the number of deaths ($z$) within a month of CABG surgeries and total number of patients ($n$) receiving CABG surgeries in each hospital. Using these data, \pkg{Rgbp} provides point and interval estimates of the true death ratio for each hospital so that one can choose the most reliable hospital. The data can be loaded into R using the following code. Note that throughout this paper, the symbol `\code{R>}' below represents a command prompt that you should not type on \proglang{R}.

\begin{CodeChunk}
\begin{CodeInput}
R> z <- c( 3, 2, 5, 11, 9, 12, 12, 4, 10, 13, 14, 7, 12, 11, 13, 22, 15, 
          11, 14, 11, 16, 14, 9, 15, 13, 35, 26, 25, 20, 35, 27)
R> n <- c(67, 68, 210, 256, 269, 274, 278, 295, 347, 349, 358, 396, 431,
         441, 477, 484, 494, 501, 505, 540, 563, 593, 602, 629, 636, 729,
         849, 914, 940, 1193, 1340)
\end{CodeInput}
\end{CodeChunk}
or
\begin{CodeChunk}
\begin{CodeInput}
R> data(hospitals)
R> z <- hospitals$d
R> n <- hospitals$n
\end{CodeInput}
\end{CodeChunk}

@@

Next, \code{gbp} will help us fit the Poisson hierarchical model with the Gamma conjugate prior distribution on the true death rate $\lambda_{j}$ whose mean is 0.020 ($\lambda_{0}=0.020$) as described in the section \ref{poissonsubsec}. For reference, the number of regression coefficients ($m$) is 0 because we do not need to estimate the prior mean via log-linear regression.
\begin{CodeChunk}
\begin{CodeInput}
R> p <- gbp(z, n, mean.PriorDist = 0.02, model = "poisson")
R> p
\end{CodeInput}
\begin{CodeOutput}
Summary for each unit (sorted by n):

@@

The output contains information about observed death ratio ($y_{j}$), caseload ($n_{j}$), known prior mean ($\lambda_{0}$), shrinkage estimate ($\hat{B}_{j}$), lower bound of interval estimate ($\hat{\lambda}_{j, low}$), posterior mean ($\hat{\lambda}_{j}=E(\lambda_{j}\vert \textbf{y})$), upper bound of interval estimate ($\hat{\lambda}_{j, upp}$), and standard deviation of posterior distribution ($sd(\lambda_{j}\vert \textbf{y})$).

@@

  post.mode.alpha post.sd.alpha
1          -5.818         0.411
\end{CodeOutput}
\end{CodeChunk}
From the output of \code{summary} we can easily calculate $\hat{r}=\textrm{exp}(5.818)=336$, which is a good indicator of how valuable and informative the hypothetical second-level hierarchy is. It means that observed sample means of hospitals whose caseloads are less than 336 will shrink toward the prior mean (0.020) more than 50\%. For example, the shrinkage estimate of the first hospital ($\hat{B}_{1}= 0.834$) was calculated by 336 / (336 + 67), where 67 is its caseload ($n_{1}$), and its posterior mean is $(1-0.834)*0.045 + 0.834 * 0.020=0.024$. As for this hospital, using more information from the prior distribution is an appropriate choice because the observed amount of information (67) is far less than the amount of state-level information (336).

To obtain a graphical summary the function \code{plot} can be used, as seen in Figure \ref{fig:hospshr}.

\begin{CodeChunk}
\begin{CodeInput}
R> plot(p)
\end{CodeInput}
\end{CodeChunk}
\begin{figure}[h]
\begin{center}
\includegraphics[scale=0.25]{hospital1.png}
\caption{Shrinkage plot and 95\% interval plot for 31 hospitals}
\label{fig:hospshr}
\end{center}
\end{figure}

@@

Also, \code{gbp} can provide interval estimates with different confidence levels, for example 90\%,  and the appropriate code adjustment is `\code{R> p <- gbp(z, n, Alpha = 0.9, mean.PriorDist = 0.02, model = "poisson")}.'  Then, the below code will evaluate whether interval estimates achieve the 90\% confidence level.

@@

In Figure \ref{fig:hospitalcoverage} we see three lines; one is a red line connecting Rao-Blackwellized unbiased estimates for 31 hospitals; another is a dashed blue line connecting simple unbiased estimates for those hospitals; the other is a black horizontal line indicating the confidence level, 0.95.

The estimated overall average coverage rate is 0.950 from both Rao-Blackwellized and simple unbiased estimates. This result shows that the interval estimates for this particular dataset accurately achieves 95\% confidence under repeated sampling. Note that these estimates depend on the given true value of $r$ and the assumption that the model is true.

If we want to check average Rao-Blackwellized unbiased estimates for each hospital, the following code gives us such estimates.
\begin{CodeChunk}
\begin{CodeInput}
R> pcv$coverageRB
\end{CodeInput}
\begin{CodeOutput}
 [1] 0.950 0.950 0.950 0.951 0.950 0.950 0.951 0.950 0.950 0.950 0.951 0.951 
[13] 0.950 0.950 0.950 0.950 0.951 0.950 0.950 0.950 0.950 0.951 0.950 0.950 
[25] 0.951 0.950 0.951 0.950 0.951 0.951 0.950
\end{CodeOutput}
\end{CodeChunk}

As for average simple unbiased estimates for each hospital, we can type the code below.
\begin{CodeChunk}
\begin{CodeInput}
R> pcv$coverageS
\end{CodeInput}
\begin{CodeOutput}
 [1] 0.949 0.953 0.946 0.955 0.957 0.939 0.956 0.957 0.944 0.952 0.956 0.955 
[13] 0.949 0.957 0.948 0.954 0.951 0.934 0.956 0.943 0.959 0.952 0.949 0.964 
[25] 0.949 0.953 0.941 0.938 0.941 0.956 0.951
\end{CodeOutput}
\end{CodeChunk}

One more thing to mention is the accuracy of Rao-Blackwellized unbiased estimates compared to that of simple ones. Taking the first hospital as an example, we can calculate the sample variance of 1,000 Rao-Blackwellized unbiased estimates for the first hospital and that of 1,000 simple ones by typing following code. For reference, \code{raw.resultRB} and \code{raw.resultS}, each row of which is about each hospital, in \code{pcv} contain all the individual simulation results.
\begin{CodeChunk}
\begin{CodeInput}
R> var(pcv$raw.resultRB[1, ])
\end{CodeInput}
\begin{CodeOutput}
 [1] 0.002031225
\end{CodeOutput}
\begin{CodeInput}
R> var(pcv$raw.resultS[1, ])
\end{CodeInput}
\begin{CodeOutput}
 [1] 0.04844745
\end{CodeOutput}
\end{CodeChunk}

@@

The Education Testing Service (ETS) conducted randomized experiments in eight separate schools (group) to test whether students (unit) SAT scores are effected by coaching. The dataset contains the estimated coaching effects on SAT scores ($y_{j}, j=1, \ldots, 8$) and standard errors ($se_{j}, j=1, \ldots, 8$) of the eight schools \citep{1981}.
\begin{CodeChunk}
\begin{CodeInput}
R> y  <- c(12, -3, 28,  7,  1,  8, 18, -1)
R> se <- c(18, 16, 15, 11, 11, 10, 10,  9)
\end{CodeInput}
\end{CodeChunk}
or
\begin{CodeChunk}
\begin{CodeInput}
R> data(schools)
R> y  <- schools$y
R> se <- schools$se
\end{CodeInput}
\end{CodeChunk}

@@

\begin{CodeChunk}
\begin{CodeInput}
R> g <- gbp(y, se, model = "gaussian")
R> g
\end{CodeInput}
\begin{CodeOutput}
Summary for each unit (sorted by se):

@@

As seen in Figure \ref{fig:schoolcoverage} the desired $95\%$ confidence (black horizontal line at 0.95) is achieved (actually, exceeded) for each school in this example. Note that all the coverage estimates depend on the given true values of $A$ and $\beta_{0}$, and the assumption that the model is true.

In addition, average Rao-Blackwellized unbiased estimates for each school can be seen as below.
\begin{CodeChunk}
\begin{CodeInput}
R> gcv$coverageRB
\end{CodeInput}
\begin{CodeOutput}
 [1] 0.966 0.957 0.966 0.962 0.960 0.961 0.960 0.969
\end{CodeOutput}
\end{CodeChunk}

As for average simple unbiased estimates for each school, 
\begin{CodeChunk}
\begin{CodeInput}
R> gcv$coverageS
\end{CodeInput}
\begin{CodeOutput}
[1] 0.970 0.943 0.957 0.968 0.956 0.969 0.961 0.976
\end{CodeOutput}
\end{CodeChunk}

All the individual simulation results are saved in \code{pcv$raw.resultRB} and \code{pcv$raw.resultS}, in which each row is about each school.

@@

The following dataset from the New York Times published on 26 April 1970 contains information on the batting averages of 18 major league baseball players through their first 45 official at-bats of the 1970 season \citep{1975}. In addition one covariate relating to the position of each player was observed and for illustrative purposes, we transform this variable into a binary indicator (1 if a player was an outfielder and 0 otherwise).
\begin{CodeChunk}
\begin{CodeInput}
R> z <- c(18, 17, 16, 15, 14, 14, 13, 12, 11, 11, 10, 10, 10, 10, 10,  9,  8,  7)
R> n <- c(45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45)
R> x <- c( 1,  1,  1,  1,  1,  0,  0,  0,  0,  1,  0,  0,  0,  1,  1,  0,  0,  0) 
\end{CodeInput}
\end{CodeChunk}
or
\begin{CodeChunk}
\begin{CodeInput}
R> data(baseball)
R> z <- baseball[, 4]
R> n <- baseball[, 3]
R> x <- ifelse(baseball$Position == "fielder", 1, 0)
\end{CodeInput}
\end{CodeChunk}

@@

%In problems where a covariate is present \code{gbp} provides a regression summary (in this example logistic regression)
\begin{CodeChunk}
\begin{CodeInput}
R> summary(b)
\end{CodeInput}
\begin{CodeOutput}
Main summary:

@@

We see that the two prior means distinguishing outfielders from other positions are significantly different (p-value = 0.038), supporting our initial belief. The positive sign of $\hat{\beta}_{1}$ indicates that the mean batting average for all the outfielders tends to be higher than that for those in the other positions.

Now, let's see following shrinkage and 95\% interval plots for more intuition. It is obvious that sample means (empty dots) on the upper horizontal line shrink towards two different means, 0.233 and 0.310. For reference, the red line symbols on dots are for when two or more points have the same mean and are plotted over each other. For example, five players (from the 11th player to the 15th) have the same sample mean (0.222) and at this point on the upper horizontal line, there are short red lines toward five directions.

\begin{CodeChunk}
\begin{CodeInput}
R> plot(b)
\end{CodeInput}
\end{CodeChunk}
\begin{figure}[h]
\begin{center}
\includegraphics[scale=0.3]{baseball1.png}
\caption{Shrinkage plot and 95\% interval plot for 18 baseball players}
\label{fig:baseball}
\end{center}
\end{figure}

@@

Then, how much can we trust these interval estimates? The following frequency method checking that regards the estimated values, $\hat{r}$ (=112.95) and $\hat{\beta}~(=(-1.194, ~0.389)^{T})$, as true values will answer it. For reference, if we want to try different true values, the appropriate code will be \code{coverage(b, A.or.r = 100, reg.coef = c(-1, 0.2), nsim = 1000)} instead of below one.
